### 2015-10-28 postdoctoral/gamma_functions.tex
prove corollary
typos
change kappa to alpha
partial lexicographic result. need to refactor for traditional \hat L

\renewcommand{\int}{\textrm{int}}
\renewcommand{\cl}{\textrm{cl}}
\newcommand{\lexTimes}{\times_{\textrm{lex}}}

@@

  \begin{proof}
    We start by placing an order on \(X\). Let \(\vec x<\vec y\) if
    there exists \(a\in L\) with \(\vec x(a)=0,\vec y(a)=1\). We claim this is
    a total order inducing the topology on \(X\).

    We first observe that if \(\vec x(b)=1\), then for all \(a\leq b\),
    \(\vec x(a)\in\nu(1)=\{1\}\). If \(\vec x\not=\vec y\), then assume
    without loss of generality that \(\vec x(a)=0,\vec y(a)=1\), so
    \(\vec x<\vec y\). Also, whenever \(\vec x(b)=1\), we have that \(b<a\),
    so \(\vec y(b)=1\), preventing \(\vec y<\vec x\). Finally if
    \(\vec x<\vec y\) and \(\vec y<\vec z\), take \(a,b\) with
    \(\vec x(a)=0\), \(\vec y(a)=1\),\(\vec y(b)=0\),\(\vec z(b)=1\). It
    follows that \(a<b\) so \(\vec z(a)=1\) and \(\vec x<\vec z\).

    Consider the basic open set \(B(\vec x,F)\) for a finite set
    \(F\in [L]^{<\omega}\)
    about the sequence \(\vec x\in X\) which contains all sequences
    \(\vec y\) agreeing with \(\vec x\) on \(F\). If \(\vec x(a)=1\) for all
    \(a\in F\), then let \(\vec w\in X\) be \(0\) on the maximum of \(F\),
    and \(1\) for anything less. It follows that
    \(B(\vec x,F)=(\vec w,\rightarrow)\). If \(\vec x(a)=0\) for all
    \(a\in F\), then let \(\vec y\in X\) be \(1\) on the minimum of \(F\),
    and \(0\) for anything greater. It follows that
    \(B(\vec x,F)=(\leftarrow,\vec y)\). Finally if \(\vec x(a)=1\) and
    \(\vec x(b)=0\) for \(a<b\) in \(F\) and nothing between \(a,b\) is in
    \(F\), then let \(\vec w\in X\) be \(0\) on \(a\)
    and \(1\) for anything less, and let \(\vec y\in X\) be \(1\) on \(b\)
    and \(0\) for anything greater. It follows that
    \(B(\vec x,F)=(\vec w,\vec y)\).

    Let \(\phi\) evaluate each \(\vec x\in X\subseteq 2^L\) as the
    characteristic function for a subset of \(L\). It's easy to see that
    \(\phi\) is an order isomorphism between \(\<X,\leq\>\) and
    \(\<\check L,\subseteq\>\).
  \end{proof}

@@

  \begin{definition}
    Let \(\varprojlim^\star\{X,f,L\}\subseteq\varprojlim\{X,f,L\}\) satisfy
    that \(\vec x(a)=\lim_{t\to a}\vec x(t)\) for all \(a\in L\)
    (for any open neighborhood
    \(U\)of \(\vec x(a)\) there is \(b<a\) where \(\vec x(t)\in U\)
    for all \(t\in(b,a]\)).
  \end{definition}

@@

    Let \(A\) be a left-open subset of \(L\). Then let \(\vec x(a)=1\) when
    \(a\in\cl A\) and \(0\) otherwise. Then \(\vec x\in Y\),
    \(\phi(\vec x)=\cl A\), and \(\int\circ\phi(\vec x)=\int\cl A=A\).

    Let \(\vec x,\vec y\in Y\). If
    \(\int\circ\phi(\vec x)=\int\circ\phi(\vec y)=A\), then \(A\) is a
    left-open set where \(\vec x(a)=\vec y(a)=1\) for \(a\in A\). It follows
    that if \(b\in\cl A\), then as \(\vec x,\vec y\in Y\),
    \(\vec x(b)=\vec y(b)=1\) as well. And if \(c\not\in\cl A\), then
    as \(c\not\in\phi(x)\),
    \(\vec x(c)=\vec y(c)=0\), so \(\vec x=\vec y\).

    Finally let \(\vec x<\vec y\), so there exists \(a\in L\) with
    \(\vec x(a)=0,\vec y(a)=1\). Then
    \(
      \int\circ\phi(\vec x)
        \subseteq
      \phi(\vec x)
        \subseteq
      (\leftarrow,a)
        \subseteq
      \int\circ\phi(\vec y)
    \). Thus \(\int\circ\phi\) preserves order.
  \end{proof}

  \begin{corollary}
    \(\varprojlim^\star \{2, \nu, \kappa\}=\kappa+1\)
  \end{corollary}

  % \begin{theorem}
  %   Let \(K\) be a compact LOTS with minimum \(0\) and maximum \(1\). Then
  %   \(Z=\varprojlim^\star \{K, \nu, L\}\cong \hat L\lexTimes K / \sim\)
  %   where \(\lexTimes\) induces the lexicographic ordering on the product,
  %   \(\<k,1\>\sim\<m,0\>\) when \(k<m\) and \((k,m)=\emptyset\).
  % \end{theorem}

  % \begin{proof}
  %   Similar to before, we introduce a linear order to \(Z\) where
  %   \(\vec x<\vec y\) if there exists \(a\in L\) where \(\vec x(a)=0\) and
  %   \(\vec y(a)>0\).
  % \end{proof}

>>>>

\renewcommand{\int}{\textrm{int}}
\renewcommand{\cl}{\textrm{cl}}
\newcommand{\lexTimes}{\times_{\textrm{lex}}}
\newcommand{\vect}{\vec}

@@

  \begin{proof}
    We start by placing an order on \(X\). Let \(\vect x<\vect y\) if
    there exists \(a\in L\) with \(\vect x(a)=0,\vect y(a)=1\). We claim this is
    a total order inducing the topology on \(X\).

    We first observe that if \(\vect x(b)=1\), then for all \(a\leq b\),
    \(\vect x(a)\in\nu(1)=\{1\}\). If \(\vect x\not=\vect y\), then assume
    without loss of generality that \(\vect x(a)=0,\vect y(a)=1\), so
    \(\vect x<\vect y\). Also, whenever \(\vect x(b)=1\), we have that \(b<a\),
    so \(\vect y(b)=1\), preventing \(\vect y<\vect x\). Finally if
    \(\vect x<\vect y\) and \(\vect y<\vect z\), take \(a,b\) with
    \(\vect x(a)=0\), \(\vect y(a)=1\),\(\vect y(b)=0\),\(\vect z(b)=1\). It
    follows that \(a<b\) so \(\vect z(a)=1\) and \(\vect x<\vect z\).

    Consider the basic open set \(B(\vect x,F)\) for a finite set
    \(F\in [L]^{<\omega}\)
    about the sequence \(\vect x\in X\) which contains all sequences
    \(\vect y\) agreeing with \(\vect x\) on \(F\). If \(\vect x(a)=1\) for all
    \(a\in F\), then let \(\vect w\in X\) be \(0\) on the maximum of \(F\),
    and \(1\) for anything less. It follows that
    \(B(\vect x,F)=(\vect w,\rightarrow)\). If \(\vect x(a)=0\) for all
    \(a\in F\), then let \(\vect y\in X\) be \(1\) on the minimum of \(F\),
    and \(0\) for anything greater. It follows that
    \(B(\vect x,F)=(\leftarrow,\vect y)\). Finally if \(\vect x(a)=1\) and
    \(\vect x(b)=0\) for \(a<b\) in \(F\) and nothing between \(a,b\) is in
    \(F\), then let \(\vect w\in X\) be \(0\) on \(a\)
    and \(1\) for anything less, and let \(\vect y\in X\) be \(1\) on \(b\)
    and \(0\) for anything greater. It follows that
    \(B(\vect x,F)=(\vect w,\vect y)\).

    Let \(\phi\) evaluate each \(\vect x\in X\subseteq 2^L\) as the
    characteristic function for a subset of \(L\). It's easy to see that
    \(\phi\) is an order isomorphism between \(\<X,\leq\>\) and
    \(\<\check L,\subseteq\>\).
  \end{proof}

@@

  \begin{definition}
    Let \(\varprojlim^\star\{X,f,L\}\subseteq\varprojlim\{X,f,L\}\) satisfy
    that \(\vect x(a)=\lim_{t\to a}\vect x(t)\) for all \(a\in L\)
    (for any open neighborhood
    \(U\)of \(\vect x(a)\) there is \(b<a\) where \(\vect x(t)\in U\)
    for all \(t\in(b,a]\)).
  \end{definition}

@@

    Let \(A\) be a left-open subset of \(L\). Then let \(\vect x(a)=1\) when
    \(a\in\cl A\) and \(0\) otherwise. Then \(\vect x\in Y\),
    \(\phi(\vect x)=\cl A\), and \(\int\circ\phi(\vect x)=\int\cl A=A\).

    Let \(\vect x,\vect y\in Y\). If
    \(\int\circ\phi(\vect x)=\int\circ\phi(\vect y)=A\), then \(A\) is a
    left-open set where \(\vect x(a)=\vect y(a)=1\) for \(a\in A\). It follows
    that if \(b\in\cl A\), then as \(\vect x,\vect y\in Y\),
    \(\vect x(b)=\vect y(b)=1\) as well. And if \(c\not\in\cl A\), then
    as \(c\not\in\phi(x)\),
    \(\vect x(c)=\vect y(c)=0\), so \(\vect x=\vect y\).

    Finally let \(\vect x<\vect y\), so there exists \(a\in L\) with
    \(\vect x(a)=0,\vect y(a)=1\). Then
    \(
      \int\circ\phi(\vect x)
        \subseteq
      \phi(\vect x)
        \subseteq
      (\leftarrow,a)
        \subseteq
      \int\circ\phi(\vect y)
    \). Thus \(\int\circ\phi\) preserves order.
  \end{proof}

  \begin{corollary}
    \(
      \varprojlim \{2, \nu, \alpha\}
      \cong
      \varprojlim^\star \{2, \nu, \alpha\}
      \cong
      \alpha+1
    \)
    for every ordinal \(\alpha\).
  \end{corollary}

  \begin{proof}
    Since \(\hat\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
    we get \(\varprojlim^\star \{2, \nu, \alpha\}
      \cong \hat\alpha =
    \alpha+1\) for free. Then observe that all leftward sets in \(\alpha\) are
    open: \(A=[0,\min(\alpha+1\setminus A))\).
    Thus we have
    \(\varprojlim \{2, \nu, \alpha\}\cong\check\alpha=\hat\alpha=\alpha+1\).
  \end{proof}

  \begin{theorem}
    Let \(M\) be a LOTS with minimum \(0\).
    \(Z=\varprojlim^\star \{M, \nu, L\}\cong \{-\infty\}\cup \hat L\lexTimes M'\)
    where \(M'=M\setminus\{0\}\),
    \(\lexTimes\) induces the lexicographic ordering on the product,
    and \(-\infty\) is a least element.
  \end{theorem}

  \begin{proof}
    Let \(\rho(\vect x)=\int\{a\in L:\exists b> a(\vect x(b)>0)\}\);
    this is obviously leftwards, and it's open since for each
    \(a\in\rho(\vect x)\), \(a\in(\leftarrow,b)\subseteq\rho(\vect x)\).
    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
    \(\rho(\vect x)=\rho(\vect y)\)
    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).

    Define \(r:Z\to \hat L\lexTimes M\)
    by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
    \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.

    We first show that \(r\) is a bijection. Let \(A\) be left-open
    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise.
  \end{proof}
